Finiteness in Cubical Type Theory

### 2020-07-05 sections/search.tex
figured out pi and sigma instances

Again, there's not any great revelation in ease of use here, but more complex
examples really benefit.
Especially when we build the full set of instances: any expression built out of

In Agda, as in Haskell, the problem of overlapping instances often presents
itself when more complex typeclass-based machinery is used.
While there are ways to deal with overlapping instances, it is usually better to
avoid them altogether, which is precisely what we do in our approach.
We provide instances for the semiring-based combinators we defined in
\todo[noline]{reference here}
, and require the user to provide an instance for their own type.
We don't, for example, provide an instance that itself searches for surjections
from other instances: this instance is not uniquely determined.

After all of that, the change to our \(\AgdaFunction{∀↯}\) is simple: we just
change the first parameter from explicit to an instance.
% \ExecuteMetaData[agda/Cardinality/Finite/Search.tex]{auto-inst}

The change to the \(\AgdaDatatype{Pauli}\) proof of cancellation isn't
groundbreaking at first:
\ExecuteMetaData[agda/Data/Pauli.tex]{cancel-auto}
But the real benefit is now we can automate proofs over \emph{tuples}, allowing
us to prove, for instance, commutativity.
\ExecuteMetaData[agda/Data/Pauli.tex]{comm-uncurried}
\subsection{Generic Currying and Uncurrying}
While we have arguably removed the bulk of the boilerplate from the automated
proofs, there is still the case of the ugly noise of currying and uncurrying.
In this section, we take inspiration from
\cite{allaisGenericLevelPolymorphic2019} to develop a small interface to generic
\(n\)-ary functions and properties.
What we provide here differs from that work in the following ways:
\begin{itemize}
  \item Our generic representation can handle dependent \(\sum\) and \(\prod\)
    types (rather than their non-dependent counterparts, \(\times\) and
    \(\rightarrow\)).
    This extension was necessary for our use case: it is mentioned in the paper
    as the obvious next step. 
  \item We implement the curry-uncurry combinators as (verified) isomorphisms.
    Since we are in a cubical setting, this gives us equivalences between the
    types, a feature not available in standard Agda.
  \item We deal with implicit and instance arguments generically.
\end{itemize}
A full explanation of our implementation is beyond the scope of this work, but
we will mention the key parts here.
First, we define a function arrow generic over the application method:
% \ExecuteMetaData[agda/Data/Product/N-ary.tex]{fun-arr}
Then, we prove that it is isomorphic to the normal function arrow:
% \ExecuteMetaData[agda/Data/Product/N-ary.tex]{fun-iso}
This step will allow us to write the curry-uncurry proofs once, and then extend
them to the three different argument forms without difficulty.

>>>>

Again, there's not any great revelation in ease of use here, but more complex
examples really benefit.
Especially when we build the full set of instances: any expression built out of
products and sums will automatically have an instance.
This will allow us, for instance, to perform proof search over tuples, which
gives us some degree of automation for proof search in tuples.
\begin{agdalisting}
  \ExecuteMetaData[agda/Snippets/Bool.tex]{and-comm}
\end{agdalisting}
\subsection{Generic Currying and Uncurrying}
While we have arguably removed the bulk of the boilerplate from the automated
proofs, there is still the case of the ugly noise of currying and uncurrying.
In this section, we take inspiration from
\cite{allaisGenericLevelPolymorphic2019} to develop a small interface to generic
\(n\)-ary functions and properties.
What we provide here differs from that work in the following ways:
\begin{itemize}
  \item Our generic representation can handle dependent \(\sum\) and \(\prod\)
    types (rather than their non-dependent counterparts, \(\times\) and
    \(\rightarrow\)).
    This extension was necessary for our use case: it is mentioned in the paper
    as the obvious next step. 
  \item We implement the curry-uncurry combinators as (verified) isomorphisms.
    Since we are in a cubical setting, this gives us equivalences between the
    types, a feature not available in standard Agda.
  \item We deal with implicit and instance arguments generically.
\end{itemize}
A full explanation of our implementation is beyond the scope of this work, but
we will mention the key parts here.
First, we define a function arrow generic over the application method:
% \ExecuteMetaData[agda/Data/Product/N-ary.tex]{fun-arr}
Then, we prove that it is isomorphic to the normal function arrow:
% \ExecuteMetaData[agda/Data/Product/N-ary.tex]{fun-iso}
This step will allow us to write the curry-uncurry proofs once, and then extend
them to the three different argument forms without difficulty.
